Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-21 WSSSPE4_report/wg_access.tex
fixing URL, removing todo
updating participants lists in working groups to be consistent

%members of the working group
Xinlian Liu, Mark Abraham, Sameer Shende, James Hetherington, Dominik Kempf, Michael R. Crusoe, Radovan Bast

@@

https://groups.google.com/forum/#!forum/continuous-integration-for-research-software

\todo{?}

>>>>

%members of the working group
\begin{itemize}
  \item Xinlian Liu <liu@hood.edu>
  \item Mark Abraham <mjab@kth.se>
  \item Sameer Shende <sameer@cs.uoregon.edu>
  \item James Hetherington <j.hetherington@ucl.ac.uk>
  \item Dominik Kempf <dominic.kempf@iwr.uni-heidelberg.de>
  \item Michael R. Crusoe <michael.crusoe@gmail.com>
  \item Radovan Bast <radovan.bast@uit.no>
\end{itemize}

@@

For more information, see \url{https://groups.google.com/forum/#!forum/continuous-integration-for-research-software}

%\todo{?}

### 2017-03-21 WSSSPE4_report/wg_alliance.tex
updating participants lists in working groups to be consistent

The participants are:
Neil Chue Hong <N.ChueHong@software.ac.uk>,
Jean Salac <jeansalac@virginia.edu>,
Radovan Bast <radovan.bast@uit.no>,
Lorraine Hwang <ljhwang@ucdavis.edu>,
Karthik Ram <karthik.ram@berkeley.edu>,
and
Peter Elmer <Peter.Elmer@cern.ch>.

>>>>

\begin{itemize}
\item Neil Chue Hong <N.ChueHong@software.ac.uk>
\item Jean Salac <jeansalac@virginia.edu>
\item Radovan Bast <radovan.bast@uit.no>
\item Lorraine Hwang <ljhwang@ucdavis.edu>
\item Karthik Ram <karthik.ram@berkeley.edu>
\item Peter Elmer <Peter.Elmer@cern.ch>
\end{itemize}

### 2017-03-21 WSSSPE4_report/wg_prototyping.tex
updating participants lists in working groups to be consistent

\begin{itemize}
  \item Santiago N\'u\~nez-Corrales, University of Illinois Urbana--Champaign
        <nunezco2@illinois.edu>
  \item Chris Sweet, University of Notre Dame <chris.sweet@nd.edu>
  \item Steven Brandt, Louisiana State University <sbrandt@cct.lsu.edu>
  \item Dominic Orchard, University of Kent <d.a.orchard@kent.ac.uk>
\end{itemize}

>>>>

\begin{itemize}
  \item Santiago N\'u\~nez-Corrales <nunezco2@illinois.edu>
  \item Chris Sweet <chris.sweet@nd.edu>
  \item Steven Brandt <sbrandt@cct.lsu.edu>
  \item Dominic Orchard <d.a.orchard@kent.ac.uk>
\end{itemize}
